%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Prathap}{Chandra}{ 
\href{mailto:prathap.chandra.754@gmail.com}{prathap.chandra.754@gmail.com} | +91 8179984864
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Vignan Institute of}
\subsection{Technology and Science}
\descript{Bachelor's Degree in Computer Science}
\location{June 2019 | Hyderabad, India}
\sectionsep

\subsection{TELANGANA BOARD OF}
\subsection{INTERMEDIATE EDUCATION}
\location{May 2015 | Hyderabad, India}
\sectionsep

\subsection{Bhashyam Public School}
\location{May 2013 | Hyderabad, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook/dd}{\bf prathap.chandra.754} \\
Github:// \href{https://github.com/Prathap-Chandra}{\bf Prathap-Chandra} \\
LinkedIn://  \href{https://www.linkedin.com/in/codefun/}{\bf codefun} \\
YouTube://  \href{https://www.youtube.com/channel/UChfA9tIKEAduV_kxuHyAIkA}{\bf Prathap Chandra} \\
Twitter://  \href{https://twitter.com/debarghya_das}{\bf prathapmoola} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{UNDERGRADUATE}
Data Structures and Algorithms\\
Database Management Systems\\
Operating Systems\\
File Structures\\
Computer Networks\\
Cloud Computing\\
Object Oriented Programming\\
Unix Tools and Scripting\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 10000 lines:}
VanillaJS, NodeJs \textbullet{} Express \textbullet{} 
React \\ \textbullet{} React Native \textbullet{} Rest APIs
\location{Databases}
\textbullet{} MySQL, NoSQL (mongoDB),
Redis(cache),Elasticsearch 
\location{Academic Experience}
\textbullet{} C \textbullet{} C++ \textbullet{} Python\\
\textbullet{} Bootstrap \textbullet{} PHP
\location{Familiar}
\textbullet{} Redux and other JS Frameworks
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{2gethr}
\descript{| Software Developer }
\location{May 2020 – Present | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working on co-working applications (for members and internal teams) and a SaaS Visitor Management Product.
\item Experience with MERN Stack and React Native Apps
\end{tightemize}
\sectionsep

\runsubsection{Yellow Messenger}
\descript{  }
\descript{ Software Engineer }
\location{Jun 2019 – Mar 2020 | Bangalore, India}
\begin{tightemize}
\item Built Chatbots for various Enterprises
\item Worked on Azure active directory Integration and Authentication
\item Worked on Microsoft Teams Adaptive Cards.
\end{tightemize}

\descript{Software Developer Intern }
\location{Jan 2019 – Jun 2019 | Bangalore, India}
\begin{tightemize}
\item During my internship i built simple bots using Dialogflow
\item Built a chatbot of HR Usecases using Yellow Messenger's BotPlatform.io
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Academic Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Projects}
\runsubsection{Vignan Information Management System}\\
\descript{A portal confined to our college which is being used for multiple purposes}
\location{Built this as part of our Mini Project}
\begin{tightemize}
\item Built this Web Application under the guidance of our Head of the Department. 
\item The main aim was to avoid the manual work and digitalize everything. \item In this Portal Students can check their Attendance and results Instantly. Faculty can Apply Leaves and HOD can either approve or reject the leave. HOD and principal can check the analysed results and attendance reports which are auto generated with just once click.
\item This Project is an extension of a project \textbf{\href{http://studentsfate.phpnet.us/}{StudentsFate}} which i built during my 2-1 semester
\end{tightemize}
\sectionsep

\runsubsection{VignanHub}\\
\descript{A Mini Facebook}
\location{Built this as part of a college level expo}
\begin{tightemize}
\item Worked on creating a web application similar to facebook.
\item In this portal students can post anything with privacy options similar to facebook.
\item Faculty can conduct online exams and and view the results instantly.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}

\runsubsection{Guess The Number}\\
\descript{A Number Guessing App built with React Native}
\vspace{\topsep}
\runsubsection{Your Goals}\\
\descript{A Simple Goal Listing App built with React Native}
\sectionsep

\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
